\subsection{Graphical User Interface}
\begin{enumerate}
 
  
	\item Splash Screen
   \begin{itemize}
     \item Splash screens are typically used by particularly large applications to notify the user that the program is in the process of loading. They provide feedback that a lengthy process is underway. Occasionally, a progress bar within the splash screen indicates the loading progress. A splash screen disappears when the application's main window appears. Splash screens may be added for a period of time and then replaced anew.The Splash screen displays the developers name and the 
     studio icon.

   \end{itemize}


\item Pause  System 
   \begin{itemize}
     \item The user will be
      prompted by an opening menu and can access the side 
     menu from pressing the (P) key at any time during gameplay.The user will be given four options at the pause menu

     \begin{enumerate}


      \item  Resume    : User can continue
      \item  Options   : User can change the sounds and brightness settings
      \item  Quit      : User can quit the game and return to the main
      \item  Save      : User can save the game
           \end{enumerate}


      \item  The user has access to all these options throughout game. These options are the minimum requirements in a menu system.E.g Games such as super Mario Brothers use these menu systems.

   \end{itemize}

\item Main Game 
   \begin{itemize}
     \item  Once the user the enters passes the splash screen they will be prompted by the main menu screen.Sketches outlined in Chapter 7 The Game.The main menu displays all options to the user before proceding.The user uses the WASD keyset to progress. 

      \begin{enumerate}
        
      \item  Single Player    : Loads the single player
      \item  Multi Player     : Loads game for two players 
      \item  Quit             : Exits the game back to the Desktop Screen
      \item  High Scores      : Displays the high Scores of the users Gam
           \end{enumerate}

   \end{itemize}
   
\end{enumerate}

