
\subsection{Introduction}
Welcome  my name is Tom치s O'Malley (G00361128@gmit.ie) I am a final year  Software Development  student studying @ Galway Mayo Institute of Technology .
 Here I will be documenting the obstactles , game design etc to my  ment for myis the Design  4th Year   endless runner for the Module Mobile Applications 3



\subsection{Objective }
To create a concrete/precise write up to develope a 3D Video Game using \href{https://unity.com/}{Unity}


\begin{center}


\setlength{\arrayrulewidth}{1mm}
\setlength{\tabcolsep}{18pt}
\renewcommand{\arraystretch}{2.5}

\begin{tabular}{ |p{3cm}|p{3cm}|p{3cm}|  }
\hline
\multicolumn{3}{|c|}{Project Overview  } \\
\hline
Component     & Tool & Developer \\
\hline
Write Up  & LaTex & Tom치s O'Malley \\
\hline
Software  & 3D Unity Modelling  & Tom치s O'Malley \\
\hline
Version Control  & GitHub  & Tom치s O'Malley \\
\hline
\end{tabular}


\end{center}




\centerline{Game fundamentals}

\begin{enumerate}
  \item Allow the player to control a specific character, that has an important
fictional/narrative role.
  \item Have game statistics and/or relational attributes with other game objects, enemies,
and/or the player character.

\item Allow the player to take on and navigate the levels using an easy-to-use user
interface.

\item Have obstacles that the player must overcome, such as enemies and bosses.
\end{enumerate}

The game holds a rich number of features and should allow me to create lots of different tests. Game testing is a huge part of our team's experience and we will apply the different methodologies to test and document their Product. Overall we were happy with the game Design Document provided by'Game Development International Ltd' which my whole team studied. Exclusive access to the game allowed to Alpha test the game.