\subsection{Development Tools}
\begin{enumerate}
 
  
	\item Unity Engine  
   \begin{itemize}
     \item Unity is a cross-platform game engine developed by Unity Technologies, first announced and released in June 2005 at Apple Inc.'s Worldwide Developers Conference as a Mac OS X-exclusive game engine. As of 2018, the engine had been extended to support more than 25 platforms.


   \end{itemize}


\item LaTex Document Editor
   \begin{itemize}
     \item LaTeX, stylized within the system as LaTeX, is a software system for document preparation. When writing, the writer uses plain text as opposed to the formatted text found in "What You See Is What You Get" word processors like Microsoft Word, LibreOffice Writer and Apple Pages
   \end{itemize}


\item Windows 10 Operating System 
   \begin{itemize}
     \item Windows 10 is a series of operating systems developed by Microsoft and released as part of its Windows NT family of operating systems. It is the successor to Windows 8.1, released nearly two years earlier, and was released to manufacturing on July 15, 2015, and broadly released for the general public on
   \end{itemize}


 \item Script Editor TextMate 
   \begin{itemize}
     \item TextMate is a general-purpose GUI text editor for macOS created by Allan Odgaard. TextMate features declarative customizations, tabs for open documents, recordable macros, folding sections, snippets, shell integration, and an extensible bundle system.
   \end{itemize}


   \item GitHub Version Control 
   \begin{itemize}
     \item GitHub, Inc. is an American multinational corporation that provides hosting for software development and version control using Git. It offers the distributed version control and source code management functionality of Git, plus its own features. 
   \end{itemize}

\item Image Editor   
   \begin{itemize}
     \item GIMP is a free and open-source raster graphics editor used for image manipulation and image editing, free-form drawing, transcoding between different image file formats, and more specialized tasks. GIMP is released under GPLv3+ license and is available for Linux, macOS, and Microsoft Windows. 
   \end{itemize}




\end{enumerate}

